Word learning at the semantics pragmatics interface

### 2020-03-06 paper/supplementary_material.Rmd
prep model priors

prior_me <- c(prior(normal(0, 10), class = Intercept),
           prior(normal(0, 10), class = b),
           prior(cauchy(0, 1), class = sd))

bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior,
          cores = 4,
          chains = 4,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_me.rds")

@@

```{r}
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

@@

>>>>

prior_me <- c(prior(normal(0, 5), class = Intercept),
           prior(normal(0, 5), class = b),
           prior(cauchy(0, 1), class = sd))

bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior_me,
          cores = 4,
          chains = 4,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_me.rds")

@@

```{r}
prior_cg <- c(prior(normal(0, 5), class = Intercept),
           prior(normal(0, 5), class = b),
           prior(cauchy(0, 1), class = sd))

bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
                    data = prior_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior_cg,
          cores = 4,
          chains = 4,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_cg.rds")

@@

Experiment 3 follwed the same procedure as Experiment 2 but involved the same objects as Experiment 1. In the beginning, one table was empty while there was an object (novel or familiar) on the other one. After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel). Next, the speaker re-appeared and made the usual request.

In the congruent condition, the familair object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left). In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent. In the incongruent condition, the novel object was present in the beginning and the familair object appeared while the speaker was away. In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).

Participants received up to 12 test trials, e
